Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-02-10 main.Rmd
minor edits in cyclic calendar algebra

**Hierarchy table** Let $H_n: (G, C, P)$ be a hierarchy model containing n linear granularities. $G_{l}$ represents the linear granularity of order l and $P(l,m)$ represents the period length of $G_{l}$ with respect to $G_{m}$ and $C_{G(l),G(m)}$ represents the cyclic granularity that relates linear granularity of order l and m, $\forall l,m \in n, l<m$.

@@

\begin{equation} \label{eq:eq7}
\begin{split}
C_{(G_l,G_m)}(z) & = L(C_{G_l,G_{l+1}}(z) + k(l, l+1)(C_{(G_{l+1},G_m)}(z))) \\  
  & =   L(C_{(G_l,G_{l+1}}(z) + k(l, l+1)[ C_{G_{l+1},G_{l+2}}(z) + k(l+1, l+2)( C_{G_{l+2}, G_m}(z))) \\
  & =  L(C_{G_l,G_{l+1}}(z) + k(l, l+1)(C_{G_{l+1},G_{l+2}}(z)) + k(l, l+1)k(l+1, l+2)(C_{G_{l+2}, G_{m}}))\\
  & =  L(C_{G_l,G_{l+1}}(z) + k(l, l+1)(C_{G_{l+1},G_{l+2}}(z)) + k(l, l+2)(C_{G_{l+2},G_{l+m}}(z)))\\
  &\vdots\\
  & = L(\sum_{i=0}^{m - l - 1} k(l, l+i)(C_{G_{l+i},G_{l+i+1}}(z)))\\
\end{split}
\end{equation}

@@

If $C_{G_{l},G_{m'}}(z)$ or $C_{G_{l},G_{m'}}(z) are multiple order-up circular granularities, they could be computed using similar approach in Section \ref{sec:all-circular}.

>>>>

**Hierarchy table** Let $H_n: (G, C, P)$ be a hierarchy model containing n linear granularities. $G_{l}$ represents the linear granularity of order l and $P(l,m)$ represents the period length of $G_{l}$ with respect to $G_{m}$ and $C_{G(l),G(m)}$ represents the cyclic granularity that relates linear granularity of order l and m, $\forall l,m \in {1, 2, \dots,n}$ and $l<m$.

@@

\begin{equation} \label{eq:eq7}
\begin{split}
C_{(G_l,G_m)}(z) & = L(C_{G_l,G_{l+1}}(z) + P(l, l+1)(C_{(G_{l+1},G_m)}(z))) \\  
  & =   L(C_{(G_l,G_{l+1}}(z) + P(l, l+1)[ C_{G_{l+1},G_{l+2}}(z) + P(l+1, l+2)( C_{G_{l+2}, G_m}(z))) \\
  & =  L(C_{G_l,G_{l+1}}(z) + P(l, l+1)(C_{G_{l+1},G_{l+2}}(z)) + P(l, l+1)P(l+1, l+2)(C_{G_{l+2}, G_{m}}))\\
  & =  L(C_{G_l,G_{l+1}}(z) + P(l, l+1)(C_{G_{l+1},G_{l+2}}(z)) + P(l, l+2)(C_{G_{l+2},G_{l+m}}(z)))\\
  &\vdots\\
  & = L(\sum_{i=0}^{m - l - 1} P(l, l+i)(C_{G_{l+i},G_{l+i+1}}(z)))\\
\end{split}
\end{equation}

@@

If $C_{G_{l},G_{m'}}(z)$ or $C_{G_{l},G_{m'}}(z)$ are multiple order-up circular granularities, they could be computed using similar approach in Section \ref{sec:all-circular}.
